### 2016-09-16 R/ITHIM.Rmd
Updated top directory Makefile
Also made a figure smaller so it looks better in the manuscript.
Worked on figure and changed permissions
I changed the permissins only so it looks nicer when using ls
Working on figure for manuscript

```{r ITHIMObjs, eval = TRUE, fig.width = 20, fig.height = 10, echo = FALSE, warning = FALSE}
compute <- TRUE

@@

for( muNonTravel in seq(1,50,length.out = 20) ){

@@

barplot(with(NHTS,table(HHS)))
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY, colour = HHS))
p  + geom_line(size = 2) + theme_bw() + scale_x_continuous(name="Non-Travel METs mean") + scale_y_continuous(name="Change in DALY (National)") + facet_grid(. ~ HHS)
```

>>>>

```{r ITHIMObjs, eval = TRUE, fig.width = 8, fig.height = 5, echo = FALSE, warning = FALSE}
compute <- TRUE

@@

for( muNonTravel in seq(1,10,length.out = 100) ){

@@

barplot(with(NHTS,table(HHS)))
p <- ggplot(DALYsTotal, aes(x = muNonTravel, y = DALY/1e3, colour = HHS))
p  + geom_line(size = 2) + theme_bw() + scale_x_continuous(name="Non-Travel METs mean (MET-hrs./week)") + scale_y_continuous(name="Change in National DALYs (Thousands)") + coord_cartesian(xlim = c(0, 10)) #+ facet_grid(. ~ HHS)
```
